---
title: "Alpha_diversity"
author: "Yujie Zhao"
date: "2023-11-01"
output: html_document
---

code tutorial: https://joey711.github.io/phyloseq/plot_richness-examples.html
```{r}
rm(list=ls())
library(phyloseq)
library(ggplot2)
data("GlobalPatterns")

GP <- prune_species(speciesSums(GlobalPatterns) > 0, GlobalPatterns)

```
Chao1: measure the community richness
Chao-1 estimator, calculated as N + S2 / (2 D) where N is the number of OTUs, S is the number of singleton OTUs and D is the number of doublet OTUs, i.e. OTUs with abundance 2.

Shannon Diversity: measure both richness and evenness
-sum(the relative abundance of each species * log(the relative abundance of each species))

InvSimpson: https://ib.bioninja.com.au/options/option-c-ecology-and-conser/c4-conservation-of-biodiver/biodiversity.html
measure both richness and evenness
N: total number of OTU in each sample
n: number of each OTU
formula: N(N-1)/sum(n(n-1))

```{r}
p1 = plot_richness(GP, measures=c("Observed", "Chao1", "Shannon", "InvSimpson"))
result = p1$data

```

